---
title: "Semantic Algorithm Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
Semantic search is data search technique focused on understanding the contextual meaning and intent behind a user's query. The goal of this semantic search algorithm is *summarising positive and negative words* in a document.

Topic-based semantic search

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(semanticalgorithm)
```



*PROCESSING THE DATA* 

First, we want to load the data we will be using for the analysis. In my case, it is a .txt file containing plain text (provided by the assingment instructions, called "Document_negative". For this, I just wrote down the path to my file. 

```{loading dataset}
data <- readLines("~/Downloads/Example_negative.txt") #creates a vector

#To create a continuos string:

text_raw <- readLines("~/Downloads/Example_negative.txt")
text <- paste(text_raw, collapse = " ") 
```

Next, we will process the text for semantic analysis. This will include detecting positive and negative words as well as summarising them for quantification. 

``` {processing text}

text <- tolower(text) #turns everything into lower case
text <- gsub("[[:punct:]]", " ", text) #remove punctuation

text <- gsub("\\s+", " ", text)
text <- trimws(text) #removes extra spaces

words <- unlist(strsplit(text, " ")) #turns words into vectors
```

To define positive words, I found a page containing 500 words with positive associations (https://www.goodgoodgood.co/articles/positive-words). I created a .txt file with a list of these words, which will not be added and processed similarly as the "Example_negative" file. 

The same was done for negative words, with the lexicon being extracted from the following page: https://www.thesaurus.com/e/writing/negative-words-that-start-with-a-r-d/

``` {create lexicon of positive and negative words}

positive_words_raw <- readLines("~/Downloads/positive_words.txt")
positive_words <- paste(positive_words_raw, collapse = " ")
positive_words <- tolower(positive_words)
positive_words <- gsub("[[:punct:]]", " ", positive_words)
positive_words <- gsub("\\s+", " ", positive_words)
positive_words <- trimws(positive_words)
Positive <- unlist(strsplit(positive_words, " ")) #"Positive" stores words as vectors

negative_words_raw <- readLines("~/Downloads/negative_words.txt")
negative_words <- paste(negative_words_raw, collapse = " ")
negative_words <- tolower(negative_words)
negative_words <- gsub("[[:punct:]]", " ", negative_words)
negative_words <- gsub("\\s+", " ", negative_words)
negative_words <- trimws(negative_words)
Negative <- unlist(strsplit(negative_words, " "))

```


Finally, to obtain the outcome of the search:
```{search}

summary <- list(
     total_words = length(words),
     positive_count = length(positives_found),
     negative_count = length(negatives_found),
     Positive = positives_found,
     Negative = negatives_found
)

summary

```
